DDSAnalytics  - Employee Trends

### 2018-04-15 msds6371-group-project-kaggle.Rmd
Add code for Q1 and added report info

Untransformed Data

When looking at plots of the raw data, there is a clear linear relationship between GrLivArea and SalePrice.  However, we can start to see there may be some issues with some of the points on Image 002, Image 003, and Image 004.  These will be explored later.

Most of the parameter estimates look good except for d3

### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

@@

@@

#### Plots of Untransformed Data
![BrkSide](images/Untransformed-BrkSide.png)*Image 001*
![Edwards](images/Untransformed-Edwards.png)*Image 002*
![NAmes](images/Untransformed-NAmes.png)*Image 003*
![Other Neighborhoods](images/Untransformed-Others.png)*Image 004*
![MLR Parameter Estimates](images/Untransformed-MLR-Estimates.png)*Image 005*
![MLR Residual Plots](images/Untransformed-MLR-Residuals.png)*Image 006*

>>>>

### Build and Fit the Model

#### Untransformed Data

Model: SalePrice = beta0 + beta1 * GrLivArea + beta2*d1 + beta3*d2 + beta4*d3 + beta5*int1 + beta6*int2 + beta7*int3

When looking at plots of the raw data, there is a clear linear relationship between GrLivArea and SalePrice on Image 001.  However, on Image 002 we can see several issues with the data:
* unequal spread on Residual vs Predicted and Studentized Residual vs Predicted, looks like the variance is increasing
* the qqplot is curved and the histogram is rather large in the middle suggesting non-normal data
* Cooks-D and Leverage show points that may have leverage and should be investigated

When looking at Image 003, most of the parameter estimates look good except for d3, int2 and int3.  The VIF for all estimates are high, the smallest being 22.  This is another sign that outliers should be investigated.

We need to perform outlier analysis and peform transformations to address equal deviation and normality.

#### Other Transformations

Log-Linear, and Linear_log were both experimented with.  None of the violations were addressed using any of these methods.  In some cases, it made the linear relationship worse with SalePrice.  For brevity, no graphs are provided for these transformations.

#### Log-Log Transformed Data

Model: SalePrice = beta0 + beta1 * LogGrLivArea + beta3*d2 + beta4*d3 + beta6*centLint2 + beta7*centLint3

For brevity, some of the interative process for analyzing the data is omitted, but summarised here.  It was found that there was no statistical difference between the BrkSide and Edwards neighborhoods, so these were combined into a single entity.  Also, to address the high VIF values, the interaction variables were centered.

### Assumptions
When looking at the Log-Log transformed data in Image 004, the linear relationship looks much better.  Also,, when looking at the fit diagnostics in Image 005, we can se that the assumptions are addressed:
1.There is a clear linear trend with explanatory variables with the LogSalePrice
1. The histogram looks better and the QQ plot as well, combined with the large number of observations, we can say the data ius normal
1. All residual plots look like a good random cloud with equal variace across the graph
1. For independence, we do not know how the data were collected, and will assume that they are independent

The fit diagnostics in Image 005 and Regression statistics in Image 006 display that all issues are addressed with the data.

#### Outlier Analysis

@@

SalePrice    = 19972  +  87.163*GrLivArea   +  68382*d1  + 54705*d2  +  -12416*d3  +  -57.412*int1  +  -32.847*int2  +  31.351*int3
LogSalePrice = 5.844  +  0.845*LogGrLivArea +  0.094*d2  + 0.219*d3  +  -0.268*centLint2  +  0.169*centLint3

@@

#### Plots of Untransformed Data
![Neighborhoods](images/image_001.PNG)*Image 001*
![Untransformed Fit Diagnostics](images/Image_002.PNG)*Image 002*
![Untransformed Proc Reg](images/image_003.PNG)*Image 003*
![Other Neighborhoods](images/Untransformed-Others.png)*Image 004*
![MLR Parameter Estimates](images/Untransformed-MLR-Estimates.png)*Image 005*
![MLR Residual Plots](images/Untransformed-MLR-Residuals.png)*Image 006*

----

#### Plots of Log-Log Data
![BrkSide](images/Log-Log-BrkSide.png)*Image 007*
![Edwards](images/Log-Log-Edwards.png)*Image 008*
![NAmes](images/Log-Log-NAmes.png)*Image 009*
![Other Neighborhoods](images/Log-Log-Others.png)*Image 010*
![MLR Parameter Estimates](images/Log-Log-MLR-Estimates.png)*Image 011*
![MLR Residual Plots](images/Log-Log-MLR-Residuals.png)*Image 012*

----
